\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-09 cfhtlens.tex
minor fix

\citet{kitching/etal:2016} chose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck values. They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}. This can be compared to the full five-parameter fit from \citet{kilbinger/etal:2013} who find $S_8=\sigma_8(\Omega_m/0.3)^{0.6} = 0.74 \pm 0.03$.   We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.  Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}.   We find the lowest conditional value of $\sigma_8 = 0.746 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.749 \pm 0.023$ for the `Baseline Limber Flat' (LF) case, a maximum change of $\Delta \sigma_8 = 0.0026 = 0.11 \sigma$.  These findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007 = 0.5\sigma$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).

>>>>

\citet{kitching/etal:2016} chose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck values. They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}. This can be compared to the full five-parameter fit from \citet{kilbinger/etal:2013} who find $S_8=\sigma_8(\Omega_m/0.3)^{0.6} = 0.74 \pm 0.03$.   We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.  Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}.   We find the lowest conditional value of $\sigma_8 = 0.746 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.749 \pm 0.023$ for the `Extended Limber Flat' (ELF) case, a maximum change of $\Delta \sigma_8 = 0.0026 = 0.11 \sigma$.  These findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007 = 0.5\sigma$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).
